---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pacta.transition.monitor.utils

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/pacta.transition.monitor.utils)](https://CRAN.R-project.org/package=pacta.transition.monitor.utils)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of pacta.transition.monitor.utils is to provide utility functions that 
enable the running of PACTA on the [Capital Transition Monitor Platform](https://platform.transitionmonitor.com/). 

These utils include functions that facilitate, for example, the logging and 
handling of warnings and errors, when functions are run in a server context. 

## Installation

You can install the development version of pacta.transition.monitor.utils like so:

``` r
#install.packages("devtools")
devtools::install_github("RMI-PACTA/pacta.transition.monitor.utils")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(pacta.transition.monitor.utils)
## basic example code
```
